A comprehensive analysis of natural sequence variation within the <i>Arabidopsis

### 2018-05-24 manuscript/manuscript.Rmd
fixed IAA tree tiplabels

IAA_data <- IAA_data[match(IAA_data$AGI, gsub(x = tree@phylo$tip.label, pattern = "\\.1",replacement = "")), ]
tree@phylo$tip.label <- IAA_data$name
  IAA_data$AGI
  IAA_data[match(IAA_data$AGI, gsub(x = tree@phylo$tip.label, pattern = "\\.1",replacement = "")), c("name", "AGI")]
tree@phylo$tip.label

>>>>

IAA_data <- IAA_data[match(gsub(x = tree@phylo$tip.label, pattern = "\\.1",replacement = ""), IAA_data$AGI), ] 
tree@phylo$tip.label <- IAA_data$name
ggtree(tree, layout = "rectangular", color = "grey") %<+% IAA_data + theme_tree() + scale_x_continuous(expand = c(0, 1.2)) + geom_tiplab(mapping = aes(color = Class), hjust = -0.25) + 
  theme(legend.position = c(.9,.7)) + 
  geom_nodelab(mapping = aes(label = round(prob,digits = 2)), nudge_x = -.3, nudge_y = .5, size = 3)
